\documentclass[11pt]{article}

% ---------- Packages ----------
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{lmodern}
\usepackage{xcolor}
\usepackage{ulem}


% ---------- Document ----------
\begin{document}

% ---------- Title ----------
\begin{center}
{\LARGE\bfseries Political bias measurement on social media platforms}\\[0.3em]
\rule{1\textwidth}{0.6pt}
\end{center}

\vspace{1cm}

\section*{Legend section}

yellow [Reading in progress]
\newline green [Reading done]
\newline Red [Reading done by need a new lecture]
\newline Blue [Good paper but not directly connect but peripheral]
\section*{Section A) All articles 2025}

% ---------- Enumerated List ----------
\begin{enumerate}[leftmargin=1.5cm,label=\arabic*.,itemsep=0.8em]

\item \textcolor{green}{\textbf{Accuracy and Political Bias of News Source Credibility Ratings by Large Language Models}}  
\textit{ACM Web Science Conference}, 2025.

\item \textcolor{green}{\textbf{Political Bias Prediction Models Focus on Source Cues, not semantics}}  
\textit{AAAI Conference on Artificial Intelligence (AR 23\%)}, 2025.

\item \textcolor{green}{\textbf{A New Computational Method for Quantification and Analysis of Media Bias in Cybersecurity Reporting}}
\textit{IEEE TRANSACTIONS ON COMPUTATIONAL SOCIAL SYSTEMS}, 2025.

\item \textcolor{green}{\textbf{Decoding News Bias: Multi Bias Detection in News Articles}}  
\textit{ACM International Conference on Natural Language Processing and Information Retrieval(AR34\%)}, 2025.

\item \textcolor{green}{\textbf{Media Source Matters More Than Content: Unveiling Political Bias in LLM-Generated Citations} } 
\textit{ACL Proceedings of the 2025 Conference on Empirical Methods in Natural Language Processing(EMNLP AR22.16\%)}, 2025.

\item  \textcolor{green}{\textbf{Crowdsourced Fact-Checking or Biased Commentary?Analyzing Political Bias in Twitter's Community Notes}}
\textit {ACM Web Conference}, 2025

\item  \textcolor{green}{\textbf{Disentangling Political Bias in Social Media Data Through Multitask Embedding Learning}}
\textit{IEEE TRANSACTIONS ON COMPUTATIONAL SOCIAL SYSTEMS}, 2025.

\item \textcolor{orange}{\textbf{Automated Detection of Media Bias Using Artificial Intelligence and Natural Language Processing: A Systematic Review}}
\textit{Sage journal Social Science Computer Review (IF2.7 or 5years IF4.2)}, 2025

\end{enumerate}

\section*{Section B) All articles 2024}

\begin{enumerate}

\item \textcolor{green}{\textbf{Measuring Political Bias in Large Language Models: What Is Said and How It Is Said}}  
\textit{ACL Proceedings of the 62nd Annual Meeting of the Association for Computational Linguistics (Acceptance Rate 21.4\%)}, 2024.

\item \textbf{News has Various Shades- Quantifying and Analyzing Media Bias at Aspect-level Granularity}  
\textit{ACM Journal on Computing and Sustainable Societies (Not yet relatively new since 2023 ? 60 papers out of 200+ below 30\% accepted since)}, 2024.

\item \textcolor{green}{\textbf{A systematic review on media bias detection: What is media bias, how it is expressed, and how to detect it}}
\textit{Elsevier Expert Systems With Applications (IF 7.5)}, 2024.

\item \textcolor{blue}{\textbf{Quantitative Measurement of Bias in AI-Generated Content: A Comprehensive Narrative Literature Review}}
\textit{IEEE International Symposium on Technology and Society (IF 5.22)}, 2024

\item \textcolor{blue}{\textbf{GPT –A comprehensive review on enabling technologies, potential applications, emerging challenges, and future directions}}
\textit{IEEE International Symposium on Technology and Society (IF 5.22)}, 2024

\item \textcolor{blue}{\textbf{Media Bias Matters: Understanding the Impact of Politically Biased News on Vaccine Attitudes in Social Media}  }
\textit{IEEE International Conference on Data Science and Advanced Analytics (AR under 25\%)}, 2024


\end{enumerate}

\section*{Section C) All articles 2023}

\begin{enumerate}

\item \textcolor{green}{\textbf{Data Driven Model to Investigate Political Bias in Mainstream Media}}  
\textit{IEEE Access}, 2023.

\item \textbf{Advancing Political Bias Detection: A Novel High-Accuracy Model}  
\textit{IEEE International Conference on Computational Intelligence and Sustainable Engineering Solutions (AR below 35\%)}, 2023.

\item \textbf{Introducing MBIB - The First Media Bias Identification Benchmark Task and Dataset Collection}  
\textit{ACM Conference on Research and Development in Information Retrieval (AC undeer 25\%)}, 2023.

\item \textcolor{blue}{\textbf{A Dataset on Media Bias in Search Queries and QuerySuggestions} } 
\textit{ACM Web Science Conference }, 2023.

\item \textcolor{blue}{\textbf{Analyzing COVID-Related Social Discourse on Twiter usingEmotion, Sentiment, Political Bias, Stance, Veracity andConspiracy Theories}}
\textit{ACM Web conference}, 2023

\item  \textcolor{green}{\textbf{A Survey on Bias Detection in Online News using Deep Learning}}
\textit{IEEE, Proceedings of the Second International Conference on Applied Artificial Intelligence and Computing(AR 26\% in 2024)}, 2023

\item \textcolor{blue}{\textbf{More human than human: measuring ChatGPT political bias}  }
\textit{Springer Nature (AI IF 13.9)}, 2023.
 
\end{enumerate}

\section*{Section D) All articles 2022}

\begin{enumerate}

\item \textcolor{green}{\textbf{Measuring Media Bias via Masked Language Modeling} } 
\textit{AAAI Conference on Web and Social Media (AR less than 25\%)}, 2022.

\end{enumerate}


\section*{Section E) All articles 2021}

\begin{enumerate}

\item \textbf{Political Bias and Factualness in News Sharing across more than 100,000 Online Communities}  
\textit{AAAI Conference onWeb and Social Media (AR betwwen 20\% and 25\%}, 2021.

\item \textbf{Do You Think It's Biased? How To Ask For The Perception Of Media Bias}  
\textit{IEEE Joint Conference on Digital Libraries (AR under 29\%)}, 2021.

\end{enumerate}

\section*{Section D) All articles 2020}

\begin{enumerate}

\item \textbf{Dancing to the Partisan Beat- A First Analysis of Political Communication on TikTok}  
\textit{ACM Conference on Web Science}, 2020.

\item \textcolor{green}{\textbf{Modeling, Quantifying and Visualizing Media Bias on Twitter}  }
\textit{IEEE Access}, 2020.

\item \textbf{We Can Detect Your Bias: Predicting the Political Ideology of News Articles}  
\textit{ACL Conference on Empirical Methods in Natural Language Processing (AR [20\%, 25\%])}, 2020.

\item \textbf{Analyzing Political Bias and Unfairness in News Articles at Different Levels of Granularity}  
\textit{ACL Natural Language Processing and Computational Social Science(AR 27.8\%)} , 2020.

\item \textbf{Detecting Media Bias in News Articles using Gaussian Bias Distributions}  
\textit{ACL the Association for Computational Linguistics: EMNLP (AR 22.2\%)}, 2020.

\item  \textcolor{yellow}{\textbf{Studying Political Bias via Word Embeddings}}
\textit{ACM Web Conference}, 2020.

\end{enumerate}

\end{document}
